\LARGE \bf Predicting Initialization Effectiveness for Trajectory Optimization

### 2014-02-14 paper.tex
change to jpg

\begin{figure}[!h]
\centering
\subfloat[initial path]{\includegraphics[width=0.38\linewidth]{figure/1.png}} \qquad
\subfloat[result path]{\includegraphics[width=0.38\linewidth]{figure/2.png}} \\
\subfloat[initial path]{\includegraphics[width=0.38\linewidth]{figure/5.pdf}} \qquad
\subfloat[result path]{\includegraphics[width=0.38\linewidth]{figure/6.pdf}}
\caption{Failure cases when using the state-of-the-art trajectory optimization method~\cite{Schulman:2013:FLO} for motion planning. (a) shows the initial path for a whole-body planning, which passes through the medial axis of the desk obstacle. (b) is the trajectory optimization outcome, which is stuck in an infeasible condition and the trajectory is pulled apart by virtue of being on both sides of an obstacle. (c) shows the initial path for the arm planning and the collision cannot be resolved in the final trajectory shown in (d). The main difference between trajectories in (c) and (d) is marked by dashed red boxes.}
\label{fig:failexamples}
\end{figure}

@@

\begin{figure*}[t]
\centering
\subfloat[jagged-dubin]{\includegraphics[width=0.26\linewidth]{figure/benchmark/jagged_dubins.png}} \qquad
\subfloat[gap-dubin]{\includegraphics[width=0.21\linewidth]{figure/benchmark/cargap_dubins.png}} \qquad
\subfloat[squared-dubin]{\includegraphics[width=0.22\linewidth]{figure/benchmark/squared_dubins.png}}
\caption{The dubins car environment for 2D experiments}
\label{fig:benchmarks1}
\end{figure*}

\begin{figure*}[t]
\centering
\subfloat[bookshelf]{\includegraphics[width=0.12\linewidth]{figure/benchmark/bookshelves.png}} \qquad
\subfloat[skew-bookshelf]{\includegraphics[width=0.12\linewidth]{figure/benchmark/bookshelves_rotate.png}} \qquad
\subfloat[countertop]{\includegraphics[width=0.16\linewidth]{figure/benchmark/countertop.png}} \qquad
\subfloat[industrial]{\includegraphics[width=0.16\linewidth]{figure/benchmark/industrial.png}} \qquad
\subfloat[industrial2]{\includegraphics[width=0.14\linewidth]{figure/benchmark/industrial2.png}}
\caption{The PR2 benchmarks for right arm planning with 22 links.}
\label{fig:benchmarks2}
\end{figure*}

\begin{figure*}[t]
\centering
\subfloat[hotel]{\includegraphics[width=0.28\linewidth]{figure/benchmark/hotel.png}} \qquad
\subfloat[kitchen]{\includegraphics[width=0.26\linewidth]{figure/benchmark/kitchen10.png}} \\
\subfloat[kitchen2]{\includegraphics[width=0.19\linewidth]{figure/benchmark/kitchen.png}} \qquad
\subfloat[livingroom]{\includegraphics[width=0.19\linewidth]{figure/benchmark/livingroom.png}} \qquad
\subfloat[livingroom2]{\includegraphics[width=0.24\linewidth]{figure/benchmark/livingroom2.png}}
\caption{The PR2 benchmarks for full-body planning with 88 links.}
\label{fig:benchmarks3}
\end{figure*}

>>>>

\begin{figure}[!h]
\centering
\subfloat[initial path]{\includegraphics[width=0.38\linewidth]{figure/1.jpg}} \qquad
\subfloat[result path]{\includegraphics[width=0.38\linewidth]{figure/2.jpg}} \\
\subfloat[initial path]{\includegraphics[width=0.38\linewidth]{figure/5.pdf}} \qquad
\subfloat[result path]{\includegraphics[width=0.38\linewidth]{figure/6.pdf}}
\caption{Failure cases when using the state-of-the-art trajectory optimization method~\cite{Schulman:2013:FLO} for motion planning. (a) shows the initial path for a whole-body planning, which passes through the medial axis of the desk obstacle. (b) is the trajectory optimization outcome, which is stuck in an infeasible condition and the trajectory is pulled apart by virtue of being on both sides of an obstacle. (c) shows the initial path for the arm planning and the collision cannot be resolved in the final trajectory shown in (d). The main difference between trajectories in (c) and (d) is marked by dashed red boxes.}
\label{fig:failexamples}
\end{figure}

@@

\begin{figure*}[t]
\centering
\subfloat[jagged-dubin]{\includegraphics[width=0.26\linewidth]{figure/benchmark/jagged_dubins.jpg}} \qquad
\subfloat[gap-dubin]{\includegraphics[width=0.21\linewidth]{figure/benchmark/cargap_dubins.jpg}} \qquad
\subfloat[squared-dubin]{\includegraphics[width=0.22\linewidth]{figure/benchmark/squared_dubins.jpg}}
\caption{The dubins car environment for 2D experiments}
\label{fig:benchmarks1}
\end{figure*}

\begin{figure*}[t]
\centering
\subfloat[bookshelf]{\includegraphics[width=0.12\linewidth]{figure/benchmark/bookshelves.jpg}} \qquad
\subfloat[skew-bookshelf]{\includegraphics[width=0.12\linewidth]{figure/benchmark/bookshelves_rotate.jpg}} \qquad
\subfloat[countertop]{\includegraphics[width=0.16\linewidth]{figure/benchmark/countertop.jpg}} \qquad
\subfloat[industrial]{\includegraphics[width=0.16\linewidth]{figure/benchmark/industrial.jpg}} \qquad
\subfloat[industrial2]{\includegraphics[width=0.14\linewidth]{figure/benchmark/industrial2.jpg}}
\caption{The PR2 benchmarks for right arm planning with 22 links.}
\label{fig:benchmarks2}
\end{figure*}

\begin{figure*}[t]
\centering
\subfloat[hotel]{\includegraphics[width=0.28\linewidth]{figure/benchmark/hotel.jpg}} \qquad
\subfloat[kitchen]{\includegraphics[width=0.26\linewidth]{figure/benchmark/kitchen10.jpg}} \\
\subfloat[kitchen2]{\includegraphics[width=0.19\linewidth]{figure/benchmark/kitchen.jpg}} \qquad
\subfloat[livingroom]{\includegraphics[width=0.19\linewidth]{figure/benchmark/livingroom.jpg}} \qquad
\subfloat[livingroom2]{\includegraphics[width=0.24\linewidth]{figure/benchmark/livingroom2.jpg}}
\caption{The PR2 benchmarks for full-body planning with 88 links.}
\label{fig:benchmarks3}
\end{figure*}
